Aracna: An Open-Source Quadruped Platform for Evolutionary Robotics

### 2012-05-21 paper_aracna/main.tex
stuff

The range of motion for the hip joint is INSERT degrees and that of the knee joint is INSERT degrees~(Figure~INSERT). The range of the knee joint technically depends on the position of the hip joint, but the effect is slight enough (less than INSERT) degrees, that it can be effectively ignored.

@@

I think we should wait until the rest of the paper is fleshed out before writing this.

>>>>

The range of motion for the hip joint is 21 degrees and that of the knee joint is 40 degrees~(Figure~INSERT).

@@

Aracna is a relatively low-cost open source platform for evolutionary robotics. The complex kinematics along with the open source nature of the robot will provide an interesting and challenging universal platform for comparing walking gait algorithms. The updated platform is modular, allowing for low-cost replacement parts and varied leg designs. Future work can include modifying a single leg to have different linkage lengths, or to replace a kinematic joint with a compliant, or flexible, joint. This platform enables testing an experimantal leg such as this without having to print a complete robot. Aracna will enable mutiple users to compare data across a single lightweight, low-cost evolutionary robotic platform.
